---
title: "LPS_DESeq-contrasts_Pdam"
author: "Mike Connelly"
date: "12/03/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/computing/projects/EAPSI_Pocillopora_LPS")
library(DESeq2)
```
```{r}
resultsNames(dds_LPS)
```

##Results contrasts between individual treatments and control samples

### LPS vs. Control
```{r}
res_LPS_ctrl <- results(dds_LPS, contrast = c("Treatment", "LPS", "control"))
###
res_LPS_ctrl$ID <- mcols(dds_LPS)$ID
res_LPS_ctrl$GeneInfo <- mcols(dds_LPS)$GeneInfo
res_LPS_ctrl$KO_terms <- mcols(dds_LPS)$KO_terms
res_LPS_ctrl$Pfam_domains <- mcols(dds_LPS)$Pfam_domains
res_LPS_ctrl$ID <- as.character(res_LPS_ctrl$ID)
res_LPS_ctrl$GeneInfo <- as.character(res_LPS_ctrl$GeneInfo)
res_LPS_ctrl$KO_terms <- as.character(res_LPS_ctrl$KO_terms)
res_LPS_ctrl$Pfam_domains <- as.character(res_LPS_ctrl$Pfam_domains)
###
write.csv(as.data.frame(res_LPS_ctrl[order(res_LPS_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_LPS_ctrl_FDR5.csv")
resfdr5_LPS_ctrl <- subset(res_LPS_ctrl, padj<0.05)
resfdr5_LPS_ctrl_up <- subset(res_LPS_ctrl, padj<0.05 & log2FoldChange>0)
resfdr5_LPS_ctrl_dn <- subset(res_LPS_ctrl, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_LPS_ctrl[order(resfdr5_LPS_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_LPS_ctrl_FDR5.csv")
write.csv(as.data.frame(resfdr5_LPS_ctrl_up[order(resfdr5_LPS_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_LPS_ctrl_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_LPS_ctrl_dn[order(resfdr5_LPS_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_LPS_ctrl_dn_FDR5.csv")
colnames(res_LPS_ctrl)
summary(resfdr5_LPS_ctrl)
```

## Results contrasts between different coral genotypes
### Houwan1 vs. Houwan2
```{r}
res_HW1_HW2 <- results(dds_LPS, contrast = c("Colony", "HW1", "HW2"))
###
res_HW1_HW2$ID <- mcols(dds_LPS)$ID
res_HW1_HW2$GeneInfo <- mcols(dds_LPS)$GeneInfo
res_HW1_HW2$KO_terms <- mcols(dds_LPS)$KO_terms
res_HW1_HW2$Pfam_domains <- mcols(dds_LPS)$Pfam_domains
res_HW1_HW2$ID <- as.character(res_HW1_HW2$ID)
res_HW1_HW2$GeneInfo <- as.character(res_HW1_HW2$GeneInfo)
res_HW1_HW2$KO_terms <- as.character(res_HW1_HW2$KO_terms)
res_HW1_HW2$Pfam_domains <- as.character(res_HW1_HW2$Pfam_domains)
###
write.csv(as.data.frame(res_HW1_HW2[order(res_HW1_HW2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_HW2_FDR5.csv")
resfdr5_HW1_HW2 <- subset(res_HW1_HW2, padj<0.05)
resfdr5_HW1_HW2_up <- subset(res_HW1_HW2, padj<0.05 & log2FoldChange>0)
resfdr5_HW1_HW2_dn <- subset(res_HW1_HW2, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_HW1_HW2[order(resfdr5_HW1_HW2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_HW2_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_HW2_up[order(resfdr5_HW1_HW2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_HW2_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_HW2_dn[order(resfdr5_HW1_HW2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_HW2_dn_FDR5.csv")
colnames(res_HW1_HW2)
summary(res_HW1_HW2)
```

### Houwan1 vs. Wanglitung1
```{r}
res_HW1_WT1 <- results(dds_LPS, contrast = c("Colony", "HW1", "WT1"))
###
res_HW1_WT1$ID <- mcols(dds_LPS)$ID
res_HW1_WT1$GeneInfo <- mcols(dds_LPS)$GeneInfo
res_HW1_WT1$KO_terms <- mcols(dds_LPS)$KO_terms
res_HW1_WT1$Pfam_domains <- mcols(dds_LPS)$Pfam_domains
res_HW1_WT1$ID <- as.character(res_HW1_WT1$ID)
res_HW1_WT1$GeneInfo <- as.character(res_HW1_WT1$GeneInfo)
res_HW1_WT1$KO_terms <- as.character(res_HW1_WT1$KO_terms)
res_HW1_WT1$Pfam_domains <- as.character(res_HW1_WT1$Pfam_domains)
###
write.csv(as.data.frame(res_HW1_WT1[order(res_HW1_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_WT1_FDR5.csv")
resfdr5_HW1_WT1 <- subset(res_HW1_WT1, padj<0.05)
resfdr5_HW1_WT1_up <- subset(res_HW1_WT1, padj<0.05 & log2FoldChange>0)
resfdr5_HW1_WT1_dn <- subset(res_HW1_WT1, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_HW1_WT1[order(resfdr5_HW1_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_WT1_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_WT1_up[order(resfdr5_HW1_WT1_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_WT1_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_WT1_dn[order(resfdr5_HW1_WT1_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_WT1_dn_FDR5.csv")
colnames(res_HW1_WT1)
summary(res_HW1_WT1)
```

### Houwan1 vs. Wanglitung2
```{r}
res_HW1_WT2 <- results(dds_LPS, contrast = c("Colony", "HW1", "WT2"))
###
res_HW1_WT2$ID <- mcols(dds_LPS)$ID
res_HW1_WT2$GeneInfo <- mcols(dds_LPS)$GeneInfo
res_HW1_WT2$KO_terms <- mcols(dds_LPS)$KO_terms
res_HW1_WT2$Pfam_domains <- mcols(dds_LPS)$Pfam_domains
res_HW1_WT2$ID <- as.character(res_HW1_WT2$ID)
res_HW1_WT2$GeneInfo <- as.character(res_HW1_WT2$GeneInfo)
res_HW1_WT2$KO_terms <- as.character(res_HW1_WT2$KO_terms)
res_HW1_WT2$Pfam_domains <- as.character(res_HW1_WT2$Pfam_domains)
###
write.csv(as.data.frame(res_HW1_WT2[order(res_HW1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_WT2_FDR5.csv")
resfdr5_HW1_WT2 <- subset(res_HW1_WT2, padj<0.05)
resfdr5_HW1_WT2_up <- subset(res_HW1_WT2, padj<0.05 & log2FoldChange>0)
resfdr5_HW1_WT2_dn <- subset(res_HW1_WT2, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_HW1_WT2[order(resfdr5_HW1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_WT2_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_WT2_up[order(resfdr5_HW1_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_WT2_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_WT2_dn[order(resfdr5_HW1_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_WT2_dn_FDR5.csv")
colnames(res_HW1_WT2)
summary(res_HW1_WT2)
```

### Houwan2 vs. Wanglitung1
```{r}
res_HW2_WT1 <- results(dds_LPS, contrast = c("Colony", "HW2", "WT1"))
###
res_HW2_WT1$ID <- mcols(dds_LPS)$ID
res_HW2_WT1$GeneInfo <- mcols(dds_LPS)$GeneInfo
res_HW2_WT1$KO_terms <- mcols(dds_LPS)$KO_terms
res_HW2_WT1$Pfam_domains <- mcols(dds_LPS)$Pfam_domains
res_HW2_WT1$ID <- as.character(res_HW2_WT1$ID)
res_HW2_WT1$GeneInfo <- as.character(res_HW2_WT1$GeneInfo)
res_HW2_WT1$KO_terms <- as.character(res_HW2_WT1$KO_terms)
res_HW2_WT1$Pfam_domains <- as.character(res_HW2_WT1$Pfam_domains)
###
write.csv(as.data.frame(res_HW2_WT1[order(res_HW2_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_WT1_FDR5.csv")
resfdr5_HW2_WT1 <- subset(res_HW2_WT1, padj<0.05)
resfdr5_HW2_WT1_up <- subset(res_HW2_WT1, padj<0.05 & log2FoldChange>0)
resfdr5_HW2_WT1_dn <- subset(res_HW2_WT1, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_HW2_WT1[order(resfdr5_HW2_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_WT1_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW2_WT1_up[order(resfdr5_HW2_WT1_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_WT1_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW2_WT1_dn[order(resfdr5_HW2_WT1_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_WT1_dn_FDR5.csv")
colnames(res_HW2_WT1)
summary(res_HW2_WT1)
```

### Houwan2 vs. Wanglitung2
```{r}
res_HW2_WT2 <- results(dds_LPS, contrast = c("Colony", "HW2", "WT2"))
###
res_HW2_WT2$ID <- mcols(dds_LPS)$ID
res_HW2_WT2$GeneInfo <- mcols(dds_LPS)$GeneInfo
res_HW2_WT2$KO_terms <- mcols(dds_LPS)$KO_terms
res_HW2_WT2$Pfam_domains <- mcols(dds_LPS)$Pfam_domains
res_HW2_WT2$ID <- as.character(res_HW2_WT2$ID)
res_HW2_WT2$GeneInfo <- as.character(res_HW2_WT2$GeneInfo)
res_HW2_WT2$KO_terms <- as.character(res_HW2_WT2$KO_terms)
res_HW2_WT2$Pfam_domains <- as.character(res_HW2_WT2$Pfam_domains)
###
write.csv(as.data.frame(res_HW2_WT2[order(res_HW2_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_WT2_FDR5.csv")
resfdr5_HW2_WT2 <- subset(res_HW2_WT2, padj<0.05)
resfdr5_HW2_WT2_up <- subset(res_HW2_WT2, padj<0.05 & log2FoldChange>0)
resfdr5_HW2_WT2_dn <- subset(res_HW2_WT2, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_HW2_WT2[order(resfdr5_HW2_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_WT2_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW2_WT2_up[order(resfdr5_HW2_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_WT2_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW2_WT2_dn[order(resfdr5_HW2_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_WT2_dn_FDR5.csv")
colnames(res_HW2_WT2)
summary(res_HW2_WT2)
```

### Wanglitung1 vs. Wanglitung2
```{r}
res_WT1_WT2 <- results(dds_LPS, contrast = c("Colony", "WT1", "WT2"))
###
res_WT1_WT2$ID <- mcols(dds_LPS)$ID
res_WT1_WT2$GeneInfo <- mcols(dds_LPS)$GeneInfo
res_WT1_WT2$KO_terms <- mcols(dds_LPS)$KO_terms
res_WT1_WT2$Pfam_domains <- mcols(dds_LPS)$Pfam_domains
res_WT1_WT2$ID <- as.character(res_WT1_WT2$ID)
res_WT1_WT2$GeneInfo <- as.character(res_WT1_WT2$GeneInfo)
res_WT1_WT2$KO_terms <- as.character(res_WT1_WT2$KO_terms)
res_WT1_WT2$Pfam_domains <- as.character(res_WT1_WT2$Pfam_domains)
###
write.csv(as.data.frame(res_WT1_WT2[order(res_WT1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_WT2_FDR5.csv")
resfdr5_WT1_WT2 <- subset(res_WT1_WT2, padj<0.05)
resfdr5_WT1_WT2_up <- subset(res_WT1_WT2, padj<0.05 & log2FoldChange>0)
resfdr5_WT1_WT2_dn <- subset(res_WT1_WT2, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_WT1_WT2[order(resfdr5_WT1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_WT2_FDR5.csv")
write.csv(as.data.frame(resfdr5_WT1_WT2_up[order(resfdr5_WT1_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_WT2_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_WT1_WT2_dn[order(resfdr5_WT1_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_WT2_dn_FDR5.csv")
colnames(res_WT1_WT2)
summary(res_WT1_WT2)
```

## Colony-specific results between control and LPS-exposed samples 
### Houwan1
```{r}
res_HW1_LPS <- results(dds_HW1, contrast = c("Treatment", "LPS", "control"))
###
res_HW1_LPS$ID <- mcols(dds_HW1)$ID
res_HW1_LPS$GeneInfo <- mcols(dds_HW1)$GeneInfo
res_HW1_LPS$KO_terms <- mcols(dds_HW1)$KO_terms
res_HW1_LPS$Pfam_domains <- mcols(dds_HW1)$Pfam_domains
res_HW1_LPS$ID <- as.character(res_HW1_LPS$ID)
res_HW1_LPS$GeneInfo <- as.character(res_HW1_LPS$GeneInfo)
res_HW1_LPS$KO_terms <- as.character(res_HW1_LPS$KO_terms)
res_HW1_LPS$Pfam_domains <- as.character(res_HW1_LPS$Pfam_domains)
###
write.csv(as.data.frame(res_HW1_LPS[order(res_HW1_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_LPS_FDR5.csv")
resfdr5_HW1_LPS <- subset(res_HW1_LPS, padj<0.05)
resfdr5_HW1_LPS_up <- subset(res_HW1_LPS, padj<0.05 & log2FoldChange>0)
resfdr5_HW1_LPS_dn <- subset(res_HW1_LPS, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_HW1_LPS[order(resfdr5_HW1_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_LPS_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_LPS_up[order(resfdr5_HW1_LPS_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_LPS_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW1_LPS_dn[order(resfdr5_HW1_LPS_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_LPS_dn_FDR5.csv")
colnames(res_HW1_LPS)
summary(resfdr5_HW1_LPS)
```

### Houwan2
```{r}
res_HW2_LPS <- results(dds_HW2, contrast = c("Treatment", "LPS", "control"))
###
res_HW2_LPS$ID <- mcols(dds_HW2)$ID
res_HW2_LPS$GeneInfo <- mcols(dds_HW2)$GeneInfo
res_HW2_LPS$KO_terms <- mcols(dds_HW2)$KO_terms
res_HW2_LPS$Pfam_domains <- mcols(dds_HW2)$Pfam_domains
res_HW2_LPS$ID <- as.character(res_HW2_LPS$ID)
res_HW2_LPS$GeneInfo <- as.character(res_HW2_LPS$GeneInfo)
res_HW2_LPS$KO_terms <- as.character(res_HW2_LPS$KO_terms)
res_HW2_LPS$Pfam_domains <- as.character(res_HW2_LPS$Pfam_domains)
###
write.csv(as.data.frame(res_HW2_LPS[order(res_HW2_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_LPS_FDR5.csv")
resfdr5_HW2_LPS <- subset(res_HW2_LPS, padj<0.05)
resfdr5_HW2_LPS_up <- subset(res_HW2_LPS, padj<0.05 & log2FoldChange>0)
resfdr5_HW2_LPS_dn <- subset(res_HW2_LPS, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_HW2_LPS[order(resfdr5_HW2_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_LPS_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW2_LPS_up[order(resfdr5_HW2_LPS_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_LPS_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_HW2_LPS_dn[order(resfdr5_HW2_LPS_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_LPS_dn_FDR5.csv")
colnames(res_HW2_LPS)
summary(resfdr5_HW2_LPS)
```

### Wanglitung1
```{r}
res_WT1_LPS <- results(dds_WT1, contrast = c("Treatment", "LPS", "control"))
###
res_WT1_LPS$ID <- mcols(dds_WT1)$ID
res_WT1_LPS$GeneInfo <- mcols(dds_WT1)$GeneInfo
res_WT1_LPS$KO_terms <- mcols(dds_WT1)$KO_terms
res_WT1_LPS$Pfam_domains <- mcols(dds_WT1)$Pfam_domains
res_WT1_LPS$ID <- as.character(res_WT1_LPS$ID)
res_WT1_LPS$GeneInfo <- as.character(res_WT1_LPS$GeneInfo)
res_WT1_LPS$KO_terms <- as.character(res_WT1_LPS$KO_terms)
res_WT1_LPS$Pfam_domains <- as.character(res_WT1_LPS$Pfam_domains)
###
write.csv(as.data.frame(res_WT1_LPS[order(res_WT1_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_LPS_FDR5.csv")
resfdr5_WT1_LPS <- subset(res_WT1_LPS, padj<0.05)
resfdr5_WT1_LPS_up <- subset(res_WT1_LPS, padj<0.05 & log2FoldChange>0)
resfdr5_WT1_LPS_dn <- subset(res_WT1_LPS, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_WT1_LPS[order(resfdr5_WT1_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_LPS_FDR5.csv")
write.csv(as.data.frame(resfdr5_WT1_LPS_up[order(resfdr5_WT1_LPS_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_LPS_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_WT1_LPS_dn[order(resfdr5_WT1_LPS_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_LPS_dn_FDR5.csv")
colnames(res_WT1_LPS)
summary(resfdr5_WT1_LPS)
```

### Wanglitung2
```{r}
res_WT2_LPS <- results(dds_WT2, contrast = c("Treatment", "LPS", "control"))
###
res_WT2_LPS$ID <- mcols(dds_WT2)$ID
res_WT2_LPS$GeneInfo <- mcols(dds_WT2)$GeneInfo
res_WT2_LPS$KO_terms <- mcols(dds_WT2)$KO_terms
res_WT2_LPS$Pfam_domains <- mcols(dds_WT2)$Pfam_domains
res_WT2_LPS$ID <- as.character(res_WT2_LPS$ID)
res_WT2_LPS$GeneInfo <- as.character(res_WT2_LPS$GeneInfo)
res_WT2_LPS$KO_terms <- as.character(res_WT2_LPS$KO_terms)
res_WT2_LPS$Pfam_domains <- as.character(res_WT2_LPS$Pfam_domains)
###
write.csv(as.data.frame(res_WT2_LPS[order(res_WT2_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT2_LPS_FDR5.csv")
resfdr5_WT2_LPS <- subset(res_WT2_LPS, padj<0.05)
resfdr5_WT2_LPS_up <- subset(res_WT2_LPS, padj<0.05 & log2FoldChange>0)
resfdr5_WT2_LPS_dn <- subset(res_WT2_LPS, padj<0.05 & log2FoldChange<0)
write.csv(as.data.frame(resfdr5_WT2_LPS[order(resfdr5_WT2_LPS$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT2_LPS_FDR5.csv")
write.csv(as.data.frame(resfdr5_WT2_LPS_up[order(resfdr5_WT2_LPS_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT2_LPS_up_FDR5.csv")
write.csv(as.data.frame(resfdr5_WT2_LPS_dn[order(resfdr5_WT2_LPS_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT2_LPS_dn_FDR5.csv")
colnames(res_WT2_LPS)
summary(resfdr5_WT2_LPS)
```

